---
title: "Course Project of Developing Data Products"
author: "jpanda111"
date: "April 25, 2018"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

## Data Overview
#### Utilize Iris data to do machine learing model and prediction

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, tidy = TRUE)
library(ggplot2)
library(caret)
library(gridExtra)
data(iris)
```

```{r iris_plot, echo = TRUE}
ggplot(data=iris, aes(x=Petal.Width, y=Petal.Length)) + geom_point(aes(color=Species),alpha=0.4) 
```

## APP Functionality Summary
### - The purpose of this app is to help you predict different Iris Species based on petal length and width respectively.
### - It has two different machine learning algorithms to do the predictions
1. LDA based Model Prediction
2. RandomForest based Model Prediction

### - It also provide the comparison of prediction results from those two models

## Model Prediction Plots
```{r pred_model, echo=TRUE}
model_lda <- train(Species ~ Petal.Length + Petal.Width, data = iris, method = "lda")
model_rf <- train(Species ~ Petal.Length + Petal.Width, data = iris, method = "rf", prox = TRUE)
```
```{r pred_plot}
number_of_points <- 100
minPLInput <- 1.0
maxPLInput <- 6.9
minPWInput <- 0.1
maxPWInput <- 2.5
set.seed(12345)
testing <- data.frame(Petal.Length=runif(number_of_points, minPLInput, maxPLInput), Petal.Width=runif(number_of_points, minPWInput, maxPWInput))
testing$pred_rf <- predict(model_rf, testing)  
testing$pred_lda <- predict(model_lda, testing)
testing$pred_same <- testing$pred_rf == testing$pred_lda
m1 <- ggplot(data=testing, aes(x=Petal.Width, y=Petal.Length)) + geom_point(aes(color=pred_lda),alpha=0.4) + ggtitle("LDA Model Prediction Plot")
m2 <- ggplot(data=testing, aes(x=Petal.Width, y=Petal.Length)) + geom_point(aes(color=pred_rf),alpha=0.4) + ggtitle("RF Model Prediction Plot")
grid.arrange(m1, m2, ncol=2,nrow=1)
```

## Model Comparison Plots
```{r comp_plot, echo = TRUE}
ggplot(data=testing, aes(x=Petal.Width, y=Petal.Length)) + geom_point(aes(color=pred_same),alpha=0.4) + ggtitle("Model Prediction Comparison Plot")
```
